Changes to police demand in COVID-19 pandemic

### 2022-03-14 docs/index.Rmd
updating n8 presentation

# Overall

>>>>

---
class: center, middle, inverse
# Conclusions

---
# Call types

- Quiet roads
- Expressions of concern
- Calls for advice
- Presence of guardians and absence of targets
- Violence drop
- No change in domestic violence

---
# Police response

- Higher % attended (denominator?)
- Faster response time
- Less time on scene

---
# Change in nature of demand

- For ASB the caller "profile" changed
- Otherwise no change

---
# Recommendations

- Further spatiotemporal analysis
- Share good practice (e.g. FHQ information to clarify rules and regulations)
- Further and more robust look at changes to domestic incidents
- Consider efficiencies (reduced time on scene)
